### 2018-11-13 Sabanci_talk/Sabanci_talk.tex
Finalish version

\newcommand{\todo}[1]{\textcolor{orange}{\texttt{TODO: #1}}} 
\newcommand{\red}[1]{\textcolor{red}{#1}} 
\newcommand{\bl}[1]{\textcolor{blue}{#1}}

@@

\begin{frame}{Gravitational waves: Einstein 1916}
  \begin{center}
\begin{tikzpicture}
            \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[height=3.5cm]{figs/Einstein1916.png}};
            %\draw<1>[red,ultra thick,rounded corners] (1.6,1) rectangle (\textheight-1cm,5);
           \uncover<3->{\draw<3->[red,thick] (1.7,0.04) rectangle (3.1,0.27);}
        \end{tikzpicture}
        \\
         \uncover<2->{Perturbations of spacetime with speed $=c$, sourced by accelerating masses.}
         \end{center}
          \begin{itemize}
 \item  \uncover<3->{Spacetime metric $g_{\mu\nu} = \eta_{\mu\nu} + h_{\mu\nu}$, \quad with $| h_{\mu\nu} | \ll 1$.}
 \item  \uncover<4->{Insert into $G_{\mu\nu} = 0$. Keep only $\mathcal{O}(h)$. Pick a gauge.} %(e.g. Lorenz).}
  \uncover<5->{\[ \Rightarrow\quad \boxed{\Box \bar{h}_{\mu\nu}= 0}, \quad \text{wave equation!} \]}
  \item \uncover<6->{\alert{Plane-waves:} $ \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{i k_\mu x^\mu}\right] =\Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/c )}\right]$.}
 \end{itemize}
\end{frame}

@@

 \begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
  Gravitational-wave emission: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
  \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
  \textcolor{white}{{\bf Binary systems:} 2 points masses in circular orbit.}
  \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
  Gravitational-wave emission: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
  \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
  {\bf Binary systems:} 2 points masses in circular orbit.
  \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\animategraphics[loop,controls,height=2.9cm]{12}{Circ_Orb-}{0}{20}};
    %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
    \onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  \mu\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
    \onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to eccentricity \bl{$e$}};
    \node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}{Compact Binary Inspirals}{Newtonian evolution}
 Define \bl{chirp mass} \hspace{1.cm} $\red{M_c} \equiv \mu^{3/5} M^{2/5} = \tfrac{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}}$ \\
 %and symmetric mass ratio\qquad $\nu \equiv \tfrac{\mu}{M} =\tfrac{m_1 m_2}{M^2}$\\
 \vspace{1mm}
  which gives, via Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$,   
 \onslide<2->
 {
  \begin{footnotesize}
  $$ \boxed{\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}}$$
  \end{footnotesize}\\
 } 
%
  \onslide<3->
  {
    {\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$\\
    %of gravitational binding energy
    \quad where $ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
  }
%
  \onslide<4->
  {
    \[ 
    \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }\hspace{2cm}
    \]
    \[
    \red{ \dot{f} \propto f^{11/3}\quad(1)}
    \]
    \begin{tikzpicture}[overlay,remember picture]
    \node[draw, red,thick,minimum width=3cm,minimum height=0.75cm] (b) at (5.9,0.85){};
    \end{tikzpicture}
  }

@@

\begin{frame}{Compact Binary Inspirals}
  \vspace{-3mm}
  Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
  \\
  \vspace{1mm}
  Fix integration constant $\tau = t_\text{coal} - t >0$. \\
  \vspace{2mm}
  Introduce \red{inspiral time}, i.e, time to \bl{coal}escence (merger)
  %
  \begin{small}
  \begin{align}
  \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
  &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn\hspace{2.7cm}
  \end{align}
  \end{small}
  \\
  \onslide<2->
  {
    Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
    \begin{small}
    \begin{align}
    \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
    &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}{ \left(\f{10\,\text{Hz}}{\red{f}} \right)^{\red{5/3}}}\quad \red{(3)}\nn\hspace{3.2cm}
    \end{align}
    \end{small}
  }
  %
  \onslide<3->
  {
    \begin{tikzpicture}[overlay,remember picture]
      \node[draw, red,thick,minimum width=9.2cm,minimum height=1.3cm] (b) at (4.2,3.35){};
      \node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.1,1){};
      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.2cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
    \end{tikzpicture}\\
    %
    %\vspace{2mm}
    Binary separation \\
    \vspace{-1mm}
    \[ 
    \tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}} \hspace{4cm}
    \]
  }
\end{frame}

@@

 \begin{frame}{GW Detectors: \red{Interferometers}}
    Two geodesics separated by $\xi^\mu$:
    %\[
    % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
    %\]
    $ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
    %\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
    \vspace{-3mm}
    \[
    \hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
    \]
    %
    %
    \onslide<2->
    {
      GW along $\mathbf{z}$: 
      \[
      h_{ij}^\text{TT} = \left(\begin{array}{cc}
				h_+ & h_\times \\
				h_\times & - h_+
				\end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
      \]
    }
    \onslide<3->
    {
      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
      \begin{small}
      \begin{align*}
	s_{12} &= \int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} \\
				    & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] \\
      s_{13} &\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]
      \end{align*}
      \end{small}
    }
    %
    \onslide<4->
    {
      \begin{tikzpicture}[overlay,remember picture]
      \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
      \end{tikzpicture}
    }
 \end{frame}

@@

\begin{frame}{L-IFO vs. $\bigtriangleup$-IFO Networks}
\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo
%
  \begin{footnotesize} 
  \begin{align*}
  \rho_{\text{tot},\red{\llcorner}} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
	  = {\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
  \rho_c &\equiv 2 h_0 \left[ \int_0^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2}, \quad \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}
  \end{align*}
  \end{footnotesize}
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=3.5cm,minimum height=0.8cm] (b) at (8.8,1.9){};
  \end{tikzpicture}
  \\
  %\vspace{2mm}
  \onslide<2->
  {
    $\bigtriangleup$ = \red{Three V-}IFOs: Einstein Telescope
    \begin{footnotesize} 
    \[
    \rho_{\text{tot},\bigtriangleup} = \left[\sum_{A=1}^3 \left(\rho^A\right)^2\right]^{1/2}  =  A \rho_c \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
    \]
    \end{footnotesize}
    \\
  }
  \onslide<3->
  Use \bl{RMS-averaged} $|Q|^2$
  \begin{footnotesize}
  \begin{align*}
  \rho_{\text{tot},\bigtriangleup} %&= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  &=\f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
  \end{align*}
  \end{footnotesize}
  \\
  %where \begin{small}$\tilde{H}_\bigtriangleup(f)\equiv A\,  \langle |Q|^2_\bigtriangleup\rangle\, h_0 f^{-7/6}= \f{3}{5} A h_0 f^{-7/6}$ \end{small}\\
  \vspace{-5mm}
  Compare with three-L network's \begin{small}$\rho_\text{tot} \approx \tfrac{4}{5}A\, h_0 \left[ \int df \ldots \right]^{1/2} $ \end{small}
  \vspace{10mm}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=5.5cm,minimum height=1.25cm] (b) at (-3.2,1.05){};
  \end{tikzpicture}
  %
  % 
\end{frame}

>>>>

\newcommand{\todo}[1]{\textcolor{orange}{\texttt{TODO: #1}}} 
\newcommand{\red}[1]{\textcolor{red}{#1}} 
\newcommand{\bl}[1]{\textcolor{blue}{#1}} 
\newcommand{\w}[1]{\textcolor{white}{#1}}

@@

\begin{frame}{Gravitational waves: Einstein 1916}
\vspace{-5mm}
\begin{center}
  \begin{tikzpicture}%[overlay,remember picture]
	      \onslide<1-4>\node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[height=3.5cm]{figs/Einstein1916.png}};
	      \onslide<2-4>{\draw[red,thick] (1.7,0.04) rectangle (3.1,0.27);}
  \end{tikzpicture}
  \\
  \vspace{5mm}
  \onslide<2->{Perturbations of spacetime with speed $=c$, sourced by accelerating masses.}
\end{center}
    %      
  \onslide<3->
  \[\text{Wave equation: } \boxed{\Box \bar{h}_{\mu\nu}= 0} \ \ \Longrightarrow
  \alert{\text{Plane-waves: }}  \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/\red{c} )}\right]
  \]
  %
 \onslide<4-> $A_{\mu\nu} $: polarization tensor, \\
 $\Longrightarrow$ \emph{only} \red{2} polarizations (\bl{transverse}):
  $\begin{array}{l} \w{A_{xx}=-A_{yy} = h_+}  \\ \w{A_{xy}=\ \ A_{yx} = h_\times} \\ \end{array}$
 \end{frame}

\begin{frame}{Gravitational waves: Einstein 1916}
\vspace{-5mm}
\begin{center}
  \begin{tikzpicture}%[overlay,remember picture]
	      \onslide<1>\node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[height=3.5cm]{figs/white_box.png}};
	      %\onslide<2-4>{\draw[red,thick] (1.7,0.04) rectangle (3.1,0.27);}
  \end{tikzpicture}
  \\
  \vspace{5mm}
  {Perturbations of spacetime with speed $=c$, sourced by accelerating masses.}
\end{center}
  %        
  %
  \[\text{Wave equation: } \boxed{\Box \bar{h}_{\mu\nu}= 0} \ \ \Longrightarrow
  \alert{\text{Plane-waves: }}  \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/\red{c} )}\right]
  \]
  %
 $A_{\mu\nu} $: polarization tensor, \\
 $\Longrightarrow$ \emph{only} \red{2} polarizations (\bl{transverse}):
  $\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$
 \begin{tikzpicture}[overlay,remember picture]
	      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,1.5cm)}]current page.center){\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
	      \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,1.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
\end{tikzpicture}
\end{frame}

@@

 \begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
  Gravitational-wave emission: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
  \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
  \textcolor{white}{{\bf Binary systems:} 2 points masses in a circular orbit $M=m_1+m_2$}
  \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
  Gravitational-wave emission: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
  \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
  {\bf Binary systems:} 2 points masses in a circular orbit $M=m_1+m_2$
  \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\animategraphics[loop,controls,height=2.9cm]{12}{Circ_Orb-}{0}{20}};
    %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
    \onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  \mu\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
    \onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to eccentricity \bl{$e$}};
    \node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}{Compact Binary Inspirals}{Newtonian evolution}
 Define \bl{chirp mass} \hspace{1.cm} $\red{M_c} \equiv \mu^{3/5} M^{2/5} = \tfrac{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}}$ \\
 %and symmetric mass ratio\qquad $\nu \equiv \tfrac{\mu}{M} =\tfrac{m_1 m_2}{M^2}$\\
 \vspace{1mm}
  which gives, via Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$,   
 \onslide<2->
 {
  \begin{footnotesize}
  $$ \boxed{\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}}$$
  \end{footnotesize}\\
 } 
%
  \onslide<3->
  {
    {\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$ (\bl{binding energy})\\
    %of gravitational binding energy
    \quad where $ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
  }
%
  \onslide<4->
  {
    \[ 
    \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }\hspace{2cm}
    \]
    \[
    \red{ \dot{f} \propto f^{11/3}\quad(1)}
    \]
    \begin{tikzpicture}[overlay,remember picture]
    \node[draw, red,thick,minimum width=3cm,minimum height=0.75cm] (b) at (5.9,0.85){};
    \end{tikzpicture}
  }

@@

\begin{frame}{Compact Binary Inspirals}
  \vspace{-3mm}
  Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
  \\
  \vspace{1mm}
  Fix integration constant $\tau = t_\text{coal} - t >0$. \\
  \vspace{2mm}
  \onslide<2->
  Introduce \red{inspiral time}, i.e, time to \bl{coal}escence (merger)
  %
  \begin{small}
  \begin{align}
  \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
  &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn\hspace{2.7cm}
  \end{align}
  \end{small}
  \\
  \onslide<3->
  {
    Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
    \begin{small}
    \begin{align}
    \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
    &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}{ \left(\f{10\,\text{Hz}}{\red{f}} \right)^{\red{5/3}}}\quad \red{(3)}\nn\hspace{3.2cm}
    \end{align}
    \end{small}
  }
  %
  \onslide<4->
      \begin{tikzpicture}[overlay,remember picture]
      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.25cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
      \onslide<5->\node[draw, red,thick,minimum width=9.5cm,minimum height=1.3cm] (b) at (4.4,3.35){};
      \onslide<5->\node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.1,1){};      
    \end{tikzpicture}\\
    %
    %\vspace{2mm}
    Binary separation \\
    \vspace{-1mm}
    \[ 
    \tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}} \hspace{4cm}
    \]
  %
\end{frame}

@@

 \begin{frame}{GW Detectors: \red{Interferometers}}{Geodesic deviation}
    Two geodesics separated by $\xi^\mu$:
    %\[
    % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
    %\]
    $ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
    %\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
    \vspace{-3mm}
    \[
    \hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
    \]
    %
    %
    \onslide<2->
    GW along $\mathbf{z}$: 
      \[
      h_{ij}^\text{TT} = \left(\begin{array}{cc}
				h_+ & h_\times \\
				h_\times & - h_+
				\end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
      \]
      \onslide<3->
      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
      \begin{tikzpicture}[overlay,remember picture]
	%\node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
	\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\includegraphics[height=2.39cm]{figs/white_box.png}};
      \end{tikzpicture}
          \begin{small}
      \begin{align*}
	\w{s_{12} }& \w{=\int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} }\\
	   &\w{ \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] }\\
      \w{s_{13}} &\w{\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]}
      \end{align*}
      \end{small}
    %
    %
 \end{frame}

 \begin{frame}{GW Detectors: \red{Interferometers}}{Geodesic deviation}
    Two geodesics separated by $\xi^\mu$:
    %\[
    % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
    %\]
    $ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
    %\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
    \vspace{-3mm}
    \[
    \hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
    \]
    %
    %
    %
    GW along $\mathbf{z}$: 
      \[
      h_{ij}^\text{TT} = \left(\begin{array}{cc}
				h_+ & h_\times \\
				h_\times & - h_+
				\end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
      \]
      %
      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
      \begin{tikzpicture}[overlay,remember picture]
	%\node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
	\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
      \end{tikzpicture}
    \onslide<2->      
      \begin{small}
      \begin{align*}
	s_{12} &= \int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} \\
				    & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] \\
      s_{13} &\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]
      \end{align*}
      \end{small}
    %
    %
 \end{frame}

@@

\begin{frame}{L-IFO vs. $\bigtriangleup$-IFO Networks}
\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo
%
  \begin{footnotesize} 
  \begin{align*}
  \rho_{\text{tot},\red{\llcorner}} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
	  = {\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
  \rho_c &\equiv 2 h_0 \left[ \int_0^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2}, \quad \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}
  \end{align*}
  \end{footnotesize}
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=3.5cm,minimum height=0.8cm] (b) at (8.8,1.9){};
  \end{tikzpicture}
  \\
  %\vspace{2mm}
  \onslide<2->
  {
    $\bigtriangleup$ = \red{Three V-}IFOs: Einstein Telescope
    \begin{footnotesize} 
    \[
    \rho_{\text{tot},\bigtriangleup} = \left[\sum_{A=1}^3 \left(\rho^A\right)^2\right]^{1/2}  =  A \rho_c \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
    \]
    \end{footnotesize}
    \\
  }
  \onslide<3->
  Use \bl{RMS-averaged} $|Q|^2$
  \begin{footnotesize}
  \begin{align*}
  \rho_{\text{tot},\bigtriangleup} %&= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  &=\f{6}{5}A\, h_0 \rho_c \\%\left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
  \end{align*}
  \end{footnotesize}
  \\
  %where \begin{small}$\tilde{H}_\bigtriangleup(f)\equiv A\,  \langle |Q|^2_\bigtriangleup\rangle\, h_0 f^{-7/6}= \f{3}{5} A h_0 f^{-7/6}$ \end{small}\\
  \vspace{-5mm}
  Compare with three-L network's \begin{small}$\rho_\text{tot} \approx \tfrac{4}{5}A\, h_0 \left[ \int df \ldots \right]^{1/2} $ \end{small}
  \vspace{10mm}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=3.cm,minimum height=0.9cm] (b) at (-3.2,0.9){};
  \end{tikzpicture}
  %
  % 
\end{frame}
